Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-02-20 paper/ms.tex
fixing typo in ms expression for the product of two terms
adding figurues to simulated data examples section

@@

@@

For this example, we will simulate two datasets using known GP models with
kernels outside of the support of a \celerite\ process.
We will use these simulations to demonstrate that, at least in these cases,
valid inferences can be made about the physical parameters of the model even
if the effective covariance function is known to be ``wrong''.

>>>>

It's worth noting that the product of two terms of the form found inside the
sum in \eq{celerite-kernel} can also be re-written as a sum with updated
parameters
\begin{eqnarray}
k_j(\tau) \, k_k(\tau) =
    e^{-\tilde{c}\,\tau}\,[
        a_+\,\cos(d_+\,\tau) + b_+\,\sin(d_+\,\tau) +
        a_-\,\cos(d_-\,\tau) + b_-\,\sin(d_-\,\tau)
    ]
\end{eqnarray}
where
\begin{eqnarray}
    \tilde{a}_{\pm} &=& \frac{1}{2}\,(a_j\,a_k \pm b_j\,b_k) \\
    \tilde{b}_{\pm} &=& \frac{1}{2}\,(b_j\,a_k \mp a_j\,b_k) \\
    \tilde{c} &=& c_j + c_k \\
    \tilde{d}_{\pm} &=& d_j \mp d_k \quad.
\end{eqnarray}

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/simulated/correct.pdf}
\caption{(left) A simulated dataset.
    (right) The inferred PSD~--~the blue contours encompass 68\% of the
    posterior mass~--~compared to the true PSD (dashed black line).
    \figurelabel{simulated-correct}}
\end{center}
\end{figure}

@@

For this example, we simulate a dataset using a known GP model with a kernel
outside of the support of a \celerite\ process.
This means that the true autocorrelation of the process can never be correctly
represented by the model that we're using to fit but we will use this example
to demonstrate that, at least in this case, valid inferences can still be made
about the physical parameters of the model.

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/simulated/wrong-qpo.pdf}
\caption{(left) A simulated dataset.
    (right) The inferred period of the process. The true period is indicated
    by the vertical orange line, the posterior inference using the correct
    model is shown as the blue dashed histogram, and the inference made using
    the ``wrong'' effective model is shown as the black histogram.
    \figurelabel{simulated-wrong}}
\end{center}
\end{figure}
